The Astropy Project: \\ Sustaining and Growing a Community-oriented Open-source Project and the Latest Major Release (v5.0) of the Core Package

### 2022-02-08 src/ms.tex
Fixed minor issue with a reference

With the goal of establishing a sustainable financial model for the Astropy
project, the Coordination Committee under the new governance charter (see \S
\ref{sec:project-governance}) established a standing Finance committee.
This committee overlooks the planning and disbursement of finances on behalf
of the project. The Astropy project accepts funds from institutions as well as
individuals through NUMFOCUS\footnote{NumFOCUS is a 501(c)(3) nonprofit that
supports and promotes world-class, innovative, open source scientific computing.},
the fiscal sponsor of the project. Previously, no direct financial support
was available for the project development, and NUMFOCUS covered the incurred
operational costs. However, transitioning to long-term financial stability meant
having an influx of funds in the form of institutional support \citep{fundmodel},
and hence the Astropy project applied for and successfully acquired several grants.
The two major ones are briefly summarized below.

>>>>

With the goal of establishing a sustainable financial model for the Astropy
project, the Coordination Committee under the new governance charter (see \S
\ref{sec:project-governance}) established a standing Finance committee.
This committee overlooks the planning and disbursement of finances on behalf
of the project. The Astropy project accepts funds from institutions as well as
individuals through NUMFOCUS\footnote{NumFOCUS is a 501(c)(3) nonprofit that
supports and promotes world-class, innovative, open source scientific computing.},
the fiscal sponsor of the project. Previously, no direct financial support
was available for the project development, and NUMFOCUS covered the incurred
operational costs. However, transitioning to long-term financial stability meant
having an influx of funds in the form of institutional support \citep{2016arXiv161003159M},
and hence the Astropy project applied for and successfully acquired several grants.
The two major ones are briefly summarized below.
